Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology

### 2021-06-04 MS/ms.Rmd
Just some notes

#### *Heterogenity Analysis: How Much Effect Size Variation Actually Exists?*
Quantifying effect size heterogenity (i.e., effect size variance) provides a pathway to explore hypotheses thought to explain why effects might vary within and across studies. Effect size heterogeneity can be thought of as the percentage of variance between effect sizes that cannot be attributable to sampling error (often as called 'total' heterogenity) @Higgins2002. It provides a formal way to assess how much variation is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance). We can only conduct such analyses if we have an estimate of the sampling variance for a given effect measure becasue only then can we quantify how much variation is the result of sampling variability. @Senior2016 has shown that total heterogenity is often extremely high in ecological and evolutionary meta-analysis (~91%), suggesting that effect measures vary widely across within and studies. Some of the variation is clearly the result of working with different species or strains, different traits and different outcome measures, however, some of this variation also arises because of methodological differences across studies

>>>>

#### *Heterogenity Analysis: How Much Effect Size Variation Actually Exists?*
Quantifying effect size heterogenity (i.e., effect size variance) provides a pathway to explore hypotheses thought to explain why effects might vary within and across studies. Effect size heterogeneity can be thought of as the percentage of variance between effect sizes that cannot be attributable to sampling error (often as called 'total' heterogenity) @Higgins2002. We can qauntify this using our multilevel meta-analytic models we describe above. Quantifying heterogenity provides a formal way to assess how much variation is the result of 'true' biological or methodological differences as opposed to simply chance (i.e., sampling variance). We can only conduct such analyses if we have an estimate of the sampling variance for a given effect measure becasue only then can we quantify how much variation is the result of sampling variability. @Senior2016 has shown that total heterogenity is often extremely high in ecological and evolutionary meta-analysis (~91%), suggesting that effect measures vary widely across within and studies. Some of the variation is clearly the result of working with different species or strains, different traits and different outcome measures, however, some of this variation also arises because of methodological differences across studies 
** NOTE THAT WE MAY WNAT TO SWITCH POSITION, INTRODUCE METEREGRESSION FIRSTs
